Gaussian Processes Autoregressive Models for the Disturbance Storm Time Index

### 2016-04-24 swsc.tex
Updates from ShareLaTeX

Before performance bench marks for \emph{OSA} $D_{st}$ prediction are run on the 63 geomagnetic storm events from 1998-2006 in \cite{Ji2012}, training and model selection of \emph{GP-AR} and \emph{GP-ARX} models on independent data sets must be performed. For this purpose we choose segments 00:00 1 January 2008 - 10:00 11 January 2008 and 00:00 15 November 2014 - 23:00 1 December 2014 for training and model selection respectively.

@@

@@

\begin{table}
      \caption[]{One Step Ahead $D_{st}$ prediction models}
         \label{table:DstModels}

>>>>

Before performance bench marks for \emph{OSA} $D_{st}$ prediction are run on the storm events in \cite{Ji2012}, training and model selection of \emph{GP-AR} and \emph{GP-ARX} models on independent data sets must be performed. For this purpose we choose segments 00:00 1 January 2008 - 10:00 11 January 2008 and 00:00 15 November 2014 - 23:00 1 December 2014 for training and model selection respectively.

@@

\subsection{Storm Events}
\citet{Ji2012}} compare a six OSA $D_{st}$ models in their paper by compiling a list of 63 geomagnetic storm events of varying strengths which occurred from 1998-2006. This serves as an important stepping stone for a systematic comparison of existing and new prediction techniques because performance metrics are averaged over a large number of storm events that occurred over a 8 year period.

@@

\begin{table}
      \caption[]{One Step Ahead $D_{st}$ prediction models compared in \citet{Ji2012}}
         \label{table:DstModels}
